Motional Quantum Ground-State Cooing of a Single Sodium Atom

### 2017-05-26 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] Combine figure 2

\begin{figure*}
  \includegraphics[height=6cm]{imgs/Na_RSC_schematic.pdf}
  \includegraphics[height=5cm]{sequence.pdf}
  \caption{(A) Energy diagram. D1 OP
    (B) Beam directions and polarizations
    (C) Sequence description
    \label{f-setup}}
\end{figure*}
\begin{figure}
  \includegraphics[width=4cm]{imgs/coupling_ax.png}
  \includegraphics[width=4cm]{imgs/heating_op.png}
  \caption{(A) Matrix elements as a function of $n$ and $\Delta n$ (showing complex dependency and zeros) (B) State changing probability. Large and increases as $n$ gets larger
    \label{f-ld}}
\end{figure}
\begin{figure*}
  \includegraphics[width=8cm]{imgs/spectrum_r.png}
  \includegraphics[width=8cm]{imgs/temp/fit_20170409_r2_0_ba.png}
  \caption{(A) (B) \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[width=8cm]{imgs/spectrum_a1.png}
  \includegraphics[width=8cm]{imgs/temp/fit_20170409_a1_0_ba.png}
  \caption{(A) (B) \label{f-axial}}
\end{figure*}

@@

As mentioned previously, the axial direction is much less confined and therefore has a much higher
effective Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx3.3$. The Raman spectrum before applying Raman sideband cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the eighth order suggesting that we have many motional states populated in this direction.

>>>>

\begin{figure*}
  \includegraphics[height=5.2cm]{imgs/Na_RSC_schematic.pdf}
  \includegraphics[height=4.5cm]{sequence.pdf}
  \caption{(A) Energy diagram. D1 OP
    (B) Beam directions and polarizations
    (C) Sequence description
    \label{f-setup}}
\end{figure*}
\begin{figure}
  \includegraphics[width=8.5cm]{imgs/fig2_raman_op.png}
  \caption{(A) Matrix elements as a function of $n$ and $\Delta n$ (showing complex dependency and zeros) (B) State changing probability. Large and increases as $n$ gets larger
    \label{f-ld}}
\end{figure}
\begin{figure*}
  \includegraphics[width=8cm]{imgs/spectrum_r.png}
  \includegraphics[width=8cm]{imgs/temp/fit_20170409_r2_0_ba.png}
  \caption{(A) (B) \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[width=8cm]{imgs/spectrum_a1.png}
  \includegraphics[width=8cm]{imgs/temp/fit_20170409_a1_0_ba.png}
  \caption{(A) (B) \label{f-axial}}
\end{figure*}

@@

The axial direction is much less confined and therefore has a much higher
effective Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx3.3$. The Raman spectrum before applying Raman sideband cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the eighth order suggesting that we have many motional states populated in this direction.
